\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2020-11-08 manuscript.Rnw
Add all sections (even if no content yet)

\pkg{hesim} is an \proglang{R} package that advances the functionality and performance of the existing software. Multiple model types are supported including cohort discrete time state transition models (DTSTMs), N-state PSMs, and individual-level continuous time state transition models (CTSTMs), encompassing both Markov (time-homogeneous and time-inhomogeneous) and semi-Markov processes. To maximize flexibility and faciliate integration of the statistical methods and economic model, parameters can be estimated either by fitting a model in \proglang{R} or by inputting parameters obtained from external sources. So that individual-level simulation and PSA can be run quickly, \pkg{Rcpp} and \pkg{data.table} are heavily utilized. After simulating costs and quality-adjusted life-years (QALYs) from a PSA, decision analysis can be performed within a cost-effectiveness framework.

@@

>>>>

\pkg{hesim} is an \proglang{R} package that advances the functionality and performance of the existing software. Multiple model types are supported including cohort discrete time state transition models (DTSTMs), N-state PSMs, and individual-level continuous time state transition models (CTSTMs), encompassing both Markov (time-homogeneous and time-inhomogeneous) and semi-Markov processes. To maximize flexibility and facilitate integration of the statistical methods and economic model, parameters can be estimated either by fitting a model in \proglang{R} or by inputting parameters obtained from external sources. So that individual-level simulation and PSA can be run quickly, \pkg{Rcpp} and \pkg{data.table} are heavily utilized. After simulating costs and quality-adjusted life-years (QALYs) from a PSA, decision analysis can be performed within a cost-effectiveness framework.

The remainder of this article is organized as follows. Section~\ref{sec:model-taxonomy} describes the economic models supported by \pkg{hesim}. An overview of the coding framework is provided in Section~\ref{sec:framework}. The next two sections contain example analyses. Section~\ref{sec:modeling-aggregate} shows how both cohort and individual models can be used in the common scenario where only aggregate level data is available. Section~\ref{sec:modeling-patient} moves to a case where richer patient level data is available and shows how partitioned survival analysis and multi-state modeling can be employed. The cost-effectiveness framework is described in Section~\ref{sec:cea} along with worked examples. Section~\ref{sec:discussion} makes comparisons to other software and discusses possible extensions. Finally, Section~\ref{sec:conclusion} concludes.

@@

%% -- Models with aggregate level data -----------------------------------------
\section{Economic modeling with aggregate level data} \label{sec:modeling-aggregate}

\subsection{Cohort model}

\subsection{Individual model}

%% -- Models with patient level data -------------------------------------------
\section{Economic modeling with patient level data} \label{sec:modeling-patient}

\subsection{Partitioned survival analysis}

\subsection{Multi-state model}

%% -- Cost-effectiveness analysis ----------------------------------------------
\section{Cost-effectiveness analysis} \label{sec:cea}

%% -- Discussion ---------------------------------------------------------------
\section{Discussion} \label{sec:discussion}

%% -- Conclusion ---------------------------------------------------------------
\section{Conclusion} \label{sec:conclusion}
